Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-11-10 papers/thesis-kirstie/thesis.tex
edits

Widom's Insertion formula Equation~\ref{widoms-insertion-formula}, then becomes
\begin{align}
	\mu_{ex} &= -k_BT\ln\left(e^{-\beta{V_{diff}}}+1\right)  \\
	         &= V_{diff} \\
             &= W_{rev}(R)
\end{align}
The quantity $<e^{-\beta{V_{diff}}}>$ can also be evaluated by considering
that it takes no energy for a hard sphere to be placed at a point
in the fluid where it does not overlap with any other spheres 
($V_{diff}=0$), but it would require infinite energy ($V_{diff}=\infty$)
to place a sphere where it would overlap another sphere. 
In this case Equation~\ref{widoms-insertion-formula} becomes
%\begin{equation}\mu_{excess}=-k_BT\ln(1-n\frac{4\pi}{3}R_{cavity}^3) &  \mbox{for} & R_{\cavity}=R\end{equation}
\begin{align}
  \mu_{excess}(R_{cavity}=R)=-k_BT\ln(1-n\frac{4\pi}{3}R^3) 
\end{align}
where the radius of the cavity $R_{cavity}$ equals the radius of a hard sphere R,
and $nV_{Sphere}$ is the probability that a sphere cannot be placed at
some random point in the homogeneous fluid of number density, $n$, without
overlapping with another sphere.

%where the radius of the cavity $R_{cavity}$ is equal to the radius of a 
%hard sphere, R, and $<e^{-\beta{V_{diff}}}>$ is evaluated using the 
%probablities that the cavity is either filled or not filled~\cite{Hansen}.
%For cavities that are much larger than one of the hard spheres, 
Forming a more general result by requiring 
continuity at the boundaries between equations for fluids with 
cavities of a radius $\operatorname{R}_{cavity}$, that is larger, or very 
much larger than the hard sphere radius R, Scaled Partical Theory arrives at an 
expression~\cite{Hansen} for the excess Helmholtz 
free energy of a homogeneous fluid in terms of the packing fraction $\eta$ 
\begin{equation}\label{Fexcess-SPT}{\frac{\beta{F_{excess}}}{N}=-ln(1-\eta)+\frac{3\eta}{1-\eta}+\frac{3{\eta}^2}{2(1-\eta)^2}}\end{equation} 
where
\begin{equation}{\eta = \frac{\mbox{Volume occupied by the spheres}}{\mbox{Total Volume}}}\end{equation}
\begin{equation}{\eta = \frac{N\frac{4}{3}\pi{R^3}}{V}}\end{equation}

>>>>

Widom's Insertion formula Equation~\ref{widoms-insertion-formula}, then becomes
\begin{align}
	\mu_{ex} &= -k_BT\ln\left(e^{-\beta{V_{diff}}}+1\right)  \\
	         &= V_{diff} \\
             &= W_{rev}(R)
\end{align}
The quantity $<e^{-\beta{V_{diff}}}>$ can also be evaluated by considering
that it takes no energy for a hard sphere to be placed at a point
in the fluid where it does not overlap with any other spheres 
($V_{diff}=0$), but it would require infinite energy ($V_{diff}=\infty$)
to place a sphere where it would overlap another sphere, as described 
in Figure~\ref{fig:p_overlap}.
In this case Equation~\ref{widoms-insertion-formula} becomes
%\begin{equation}\mu_{excess}=-k_BT\ln(1-n\frac{4\pi}{3}R_{cavity}^3) &  \mbox{for} & R_{\cavity}=R\end{equation}
\begin{align}
  \mu_{excess}(R_{cavity}=R)=-k_BT\ln(1-n\frac{4\pi}{3}R^3) 
\end{align}
where the radius of the cavity $R_{cavity}$ equals the radius of a hard sphere R,
and $nV_{Sphere}$ is the probability that a sphere cannot be placed at
some random point in the homogeneous fluid of number density, $n$, without
overlapping with another sphere.

%where the radius of the cavity $R_{cavity}$ is equal to the radius of a 
%hard sphere, R, and $<e^{-\beta{V_{diff}}}>$ is evaluated using the 
%probablities that the cavity is either filled or not filled~\cite{Hansen}.
%For cavities that are much larger than one of the hard spheres, 
Forming a more general result by requiring 
continuity at the boundaries between equations written for fluids with 
cavities of a radius $\operatorname{R}_{cavity}$, that is larger, or very 
much larger than the hard sphere radius R, Scaled Partical Theory arrives at an 
expression~\cite{Hansen} for the excess Helmholtz 
free energy of a homogeneous fluid in terms of the packing fraction $\eta$ 
\begin{equation}\label{Fexcess-SPT}{\frac{\beta{F_{excess}}}{N}=-ln(1-\eta)+\frac{3\eta}{1-\eta}+\frac{3{\eta}^2}{2(1-\eta)^2}}\end{equation} 
where
\begin{equation}{\eta = \frac{\mbox{Volume occupied by the spheres}}{\mbox{Total Volume}}}\end{equation}
\begin{equation}{\eta = \frac{N\frac{4}{3}\pi{R^3}}{V}}\end{equation}
